Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-06 paper.tex
update

In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach. In particularly, we show that our proposed approach can produce solutions that results better matchmaking , which meets user's goal better. In particularly, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ in the comprehensive quality awareness approach and QoS awareness approach are compared to reveal how good our evaluation mode in Table \ref{decisionTable}. In each task, we compare $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$, and $Q_{QoS}$ is normalised to make it comparable to another method in our comprehensive awareness approach

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware appraoch}
\label{decisionTable}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$Q_{mt}$   & .232635              & .232635                          \\ \cline{2-4} 
                                      &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
\multirow{3}{*}{Task2}  &$Q_{mt}$   & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                      &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
\multirow{3}{*}{Task3}  &$Q_{mt}$   & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                 \\ \hline
\multirow{3}{*}{Task4}  &$Q_{mt}$   & .919678              & .943406$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .000000              & .000009$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480818              & .472485$\downarrow$                 \\ \hline
\multirow{3}{*}{Task5}  &$Q_{mt}$   & .000094              & .000109$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .927476              & .930975$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .476236              & .475128$\downarrow$                 \\ \hline                                                   
\end{tabular}
\end{table}
In Table \ref{decisionTable}, Task 1 represents the same solution using different methods where the values of $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ are all the same. It is due to the size of dataset 01 is very small in both available services and ontologies. However, As the size of dataset increase, we can recognise a trade-offs in task 2 using our evaluation approach, where a 0.021668 increase in similarity quality and a 0.00098 decrease in matchType quality with weights 0.4 and 0.1 respectively so that solution to task 2 is still considered to be an improvement in the functional quality part while a decrease value of 0.007249 in QoS. In task 3, the benefit of functional part quality is clearer with an increase value of 0.056648 and 0.078862 in  similarity quality and matchType quality respectively while a slight decrease in QoS. later on, the rest tasks perform the same behaviour in $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ as task 3. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

To visually compare the results generated from two evaluation approaches, we demonstrate the differences in the solutions of two composition weighted graphs under two different methods. The Fig. \ref{comparison} shows two composition weighted graphs, which are the solutions to Task 3 for(1) QoS-aware approach and $(2)$ Comprehensive quality-aware method and respectively. It can be observed that two composition weighted graphs have exactly the same workflow structure, in which the same service vertex and edges are different denoted in red. Meanwhile, we make a comparison of those different edges weights representing the quality of semantic matchmaking in Table \ref{comparisontable},as well as QoS. We can see edges obtain better semantic matchmaking quality with a reasonable trade-off in QoS

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{comparision.pdf}}}
 \caption{Example Comparison of solutions to Task 3 under different approaches.}
 \label{comparison}
\end{figure}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{Comparison of Composition Weighted Graphs}
\label{comparisontable}
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{Quality criteria} & Weighted Graph $(1)$ & Weighted Graph $(2)$ &  $\Delta Q$\\ \hline
\multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
                    & $q(e_{s})$   &1        &1                       &0\\ \hline
\multirow{2}{*}{e2} & $q(e_{mt})$  &0.75     &0.9167                  &+0.1667 \\ \cline{2-5} 
                    & $q(e_{s})$   &0.9232   &0.9630                &+0.0398\\ \hline
\multirow{2}{*}{e3} &  $q(e_{mt})$ &0.75     &0.8333                 &+0.08333\\ \cline{2-5} 
                    &   $q(e_{s})$ &0.8230   &0.9608                 &+0.1378\\ \hline
\multirow{2}{*}{e4} & $q(e_{mt})$  &0.75     &0.875                  &+0.125\\ \cline{2-5} 
                    &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
\multicolumn{2}{|l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
\end{tabular}
\end{table}

>>>>

In this section, we analyse the composition solution generated by using our approach comparing with QoS-aware approach. In particularly, we show that our proposed approach can produce solutions that results better matchmaking, which meets user's goal better.

First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}, where QoS-aware approach record $Q_{mt}$, $Q_{s}$ while utilise fitness function $Fitness = w_1A + w_2R + w_3(1 - T) + w_4(1 - C)$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, and its $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach. We observe an interesting pattern from the Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those of QoS-aware approach in Task 1, 3, 4, and 5 with an exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still considered to be higher in our approach with 0.1 and 0.4 weights respectively. However, the mean value $Q_{QoS}$ at optimum at 100th generation of QoS-aware approach can obtain a slightly higher value than that of our approach. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
\label{decisionTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{2}{|c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686  &0.220594 $\pm$ 0.009318 $\uparrow$ \\ \cline{2-4} 
                        &$Q_{s}$    &0.884962 $\pm$ 0.014140   &0.893713 $\pm$ 0.007769  $\uparrow$ \\ \cline{2-4}
                        &$Q_{QoS}$  &0.278730 $\pm$ 0.007786     &0.279548 $\pm$ 0.007627                          \\ \hline
\multirow{3}{*}{Task2}  &$Q_{mt}$   &0.001795 $\pm$ 0.000719 $\uparrow$    &0.001135 $\pm$ 0.000633  \\ \cline{2-4} 
                        &$Q_{s}$    &0.906971 $\pm$ 0.005855     &0.927965 $\pm$ 0.007306 $\uparrow$   \\ \cline{2-4}
                        &$Q_{QoS}$  &0.239979 $\pm$ 0.000578 $\uparrow$     &0.237845 $\pm$ 0.001439 \\ \hline
\multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &  0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$Q_{s}$    & 0.949109 $\pm$ 0.002331           &   0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$Q_{QoS}$  &  0.247002 $\pm$ 0.000661 $\uparrow$             &  0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$Q_{mt}$   &              &                 \\ \cline{2-4} 
                        &$Q_{s}$    &               &                   \\ \cline{2-4}
                        &$Q_{QoS}$  &               &                     \\ \hline
\multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030     &  0.000078 $\pm$ 0.000031 $\uparrow$           \\ \cline{2-4} 
                        &$Q_{s}$    &  0.915933 $\pm$ 0.012888      &  0.928189 $\pm$ 0.002486 $\uparrow$                 \\ \cline{2-4}
                        &$Q_{QoS}$  & 0.238189 $\pm$ 0.000240$\uparrow$      &  0.237232 $\pm$  0.000391  \\ \hline                                                   
\end{tabular}
\end{table}

Second, to compare the results generated from two evaluation approaches, we demonstrate an example solution that shows the differences in two composition weighted graphs representations under two different methods. The Fig. \ref{comparison} shows two composition weighted graphs as the solutions to Task 3 with $(1)$ QoS-aware approach and $(2)$ Comprehensive quality-aware method. Two approaches generate exactly the same service workflow structure while some service vertex and edges denoted in red are different part. Therefore, we make a comparison of the quality among these different edges ($e_1$ to $e4$) associated service vertex in terms of quality of semantic matchmaking and QoS attributes. We also look at $\Delta Q$ which reveals the amount of variation between two methods, where the positive values means the benefits gained under our approach while the negative values means the trade-off. There is an consistency in our methods that edges are with higher values and service vertex with slightly lower QoS. To demonstrate the benefits of the positive value, we shows our methods have better quality in semantic making in Fig. \ref{}.

\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=6cm]{comparision.pdf}}}
 \caption{Example Comparison of solutions to Task 3 under different approaches.}
 \label{comparison}
\end{figure}
\vspace{0.3cm}
\begin{figure}
\centerline{
\fbox{
\includegraphics[width=4cm]{comparisontaxonomy.pdf}}}
 \caption{Example Comparison of solutions to Task 3 under different approaches.}
 \label{comparison}
\end{figure}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{Comparison of Composition Weighted Graphs}
\label{comparisontable}
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{2}{|l|}{\shortstack{Quality \\ Criteria}} & WG $(1)$ & WG $(2)$ &  $\Delta Q$\\ \hline
\multirow{2}{*}{e1} &$q(e_{mt})$   &1        &1                       &0     \\ \cline{2-5} 
                    & $q(e_{s})$   &1        &1                       &0\\ \hline
\multirow{2}{*}{e2} & $q(e_{mt})$  &0.75     &0.9167                  &+0.1667 \\ \cline{2-5} 
                    & $q(e_{s})$   &0.9232   &0.9630                &+0.0398\\ \hline
\multirow{2}{*}{e3} &  $q(e_{mt})$ &0.75     &0.8333                 &+0.08333\\ \cline{2-5} 
                    &   $q(e_{s})$ &0.8230   &0.9608                 &+0.1378\\ \hline
\multirow{2}{*}{e4} & $q(e_{mt})$  &0.75     &0.875                  &+0.125\\ \cline{2-5} 
                    &  $q(e_{s})$  &0.9090   &0.9167                 &+0.0077\\ \hline
\multicolumn{2}{|l|}{QoS} &0.4949            &0.4915                 &-0.0034  \\ \hline
\end{tabular}
\end{table}
